This page and the next page should be removed

### 2022-01-25 analysis/manuscript.Rmd
Fix condition assignment and models

# Directory paths
data_dir <- here("data")
output_dir <- here("output")
```

@@

        # Informed condition: Matching keywords and positive response
        "Informed" =
          item_id[phase == "Insight" & keywords == "Match" & response >= 3],

        # Naive condition: Non-matching keywords and negative response
        "Naive" =
          item_id[phase == "Insight" & keywords == "Non-match" & response <= 2],

        # Exclude: Matching keywords and negative response
        "Exclude_informed" =
          item_id[phase == "Insight" & keywords == "Match" & response <= 2],

        # Exclude: Non-matching keywords and positive response
        "Exclude_naive" =
          item_id[phase == "Insight" & keywords == "Non-match" & response >= 3],

@@

# Process EEG data
res <- pipeline$group_pipeline(
  vhdr_files = vhdr_files,
  log_files = logs,
  export_dir = output_dir,
  downsample_sfreq = 250.,
  # bad_channels = "auto",
  ocular_correction = "fastica",
  highpass_freq = 0.1,
  lowpass_freq = 40.,
  triggers = c(221, 222),
  epochs_tmin = -0.5,
  epochs_tmax = 1.5,
  baseline = c(-0.2, 0.0),
  reject_peak_to_peak = 200.,
  reject_flat = 1.,
  components = list(
    "name" = c("P1", "N170", "N400"),
    "tmin" = c(0.1, 0.15, 0.4),
    "tmax" = c(0.15, 0.2, 0.7),
    "roi" = list(
      c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
      c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
      c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
    )
  ),
  average_by = c("phase/condition"),
  perform_tfr = TRUE,
  perm_contrasts = list(
    c("Pre-insight/Informed", "Pre-insight/Naive"),
    c("Insight/Informed", "Insight/Naive"),
    c("Post-insight/Informed", "Post-insight/Naive")
  ),
  n_jobs = 1
)

# Extract results
trials <- tibble(res[[1]])
evokeds <- tibble(res[[2]])
clusters <- tibble(res[[3]])
tfr_evokeds <- tibble(res[[4]])
tfr_clusters <- tibble(res[[5]])
```

```{r, modeling, eval=run$modeling}
# Read single trial data
read_csv(here(output_dir, "all_trials.csv"), col_types = cols(
  participant_id = col_factor(),
  item_id = col_factor(),
  phase = col_factor(),
  condition = col_factor()
)) %>%
  # Subset only the relevant conditions
  mutate(condition = factor(
    condition,
    levels = c("Informed", "Naive", "Excl_informed")
  )) %>%
  drop_na() -> trials

# Contrast coding for phase
cbind(
  c("Pre-insight" = -1, "Insight" = 1, "Post-insight" = 0),
  c("Pre-insight" = 0, "Insight" = -1, "Post-insight" = 1)
) %>%
  t() %>%
  ginv() -> contrasts(trials$phase)

# Contrast coding for condition
cbind(
  c("Informed" = 1, "Naive" = -1, "Excl_informed" = 0),
  c("Informed" = 1, "Naive" = 0, "Excl_informed" = -1)
) %>%
  t() %>%
  ginv() -> contrasts(trials$condition)

# Prepare model formula
mod_formula <- N170 ~ phase * condition +
  (phase * condition | participant_id) +
  (phase * condition | item_id)

# Fit linear mixed models
deps <- c("P1", "N170", "N400")
mod_lists <- map(deps, function(dep, mod_formula = form, mod_data = trials) {

  # Find the best fitting model (see Matuschek et al., 2017, *JML*)
  # Uses parallelization across all available CPU cores
  n_cores <- detectCores()
  cl <- makeCluster(n_cores)
  build <- buildmer(
    buildmerControl = buildmerControl(
      formula = mod_formula,
      data = mod_data,
      # args = list("control" = lmerControl(
      #   optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)
      # )),
      direction = c("order", "backward"),
      cl = cl,
      elim = LRTalpha(.20),
      calc.anova = TRUE,
      ddf = "Satterthwaite",
      dep = dep
    )
  )
  stopCluster(cl)

@@

  # Create list of returns
  list(
    "model" = build@model,
    "summary" = build@summary,
    "anova" = build@anova,
    "means" = em$emmeans,
    "contrasts" = em$contrasts
  ) %>%
    return()
}) %>%
  # Add ERP component names
  set_names(deps)

# Save models
saveRDS(mod_lists, here(output_dir, "models.RDS"))
```

>>>>

# Directory paths
data_dir <- here("data")
output_dir <- here("output")

# File paths
trials_file <- here(output_dir, "all_trials.csv")
models_file <- here(output_dir, "models.RDS")
```

@@

        # Informed condition: Matching keywords and positive response
        "Informed" = item_id[
          phase == "Insight" & keywords == "Match" & response %in% c(3, 4)
        ],

        # Naive condition: Non-matching keywords and negative response
        "Naive" = item_id[
          phase == "Insight" & keywords == "Non-match" & response %in% c(1, 2)
        ],

        # Exclude: Matching keywords and negative response
        "Exclude_informed" = item_id[
          phase == "Insight" & keywords == "Match" & response %in% c(1, 2)
        ],

        # Exclude: Non-matching keywords and positive response
        "Exclude_naive" = item_id[
          phase == "Insight" & keywords == "Non-match" & response %in% c(3, 4)
        ],

@@

# Process EEG data
res <- pipeline$group_pipeline(
  vhdr_files = vhdr_files,
  log_files = logs,
  export_dir = output_dir,
  downsample_sfreq = 256.,
  # bad_channels = "auto",
  ocular_correction = "fastica",
  highpass_freq = 0.1,
  lowpass_freq = 30.,
  triggers = c(221, 222),
  epochs_tmin = -0.5,
  epochs_tmax = 1.5,
  baseline = c(-0.2, 0.0),
  reject_peak_to_peak = 200.,
  reject_flat = 1.,
  components = list(
    "name" = c("P1", "N170", "N400"),
    "tmin" = c(0.1, 0.15, 0.4),
    "tmax" = c(0.15, 0.2, 0.7),
    "roi" = list(
      c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
      c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
      c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
    )
  ),
  average_by = c("phase/condition"),
  perform_tfr = FALSE,
  perm_contrasts = list(
    c("Pre-insight/Informed", "Pre-insight/Naive"),
    c("Insight/Informed", "Insight/Naive"),
    c("Post-insight/Informed", "Post-insight/Naive")
  ),
  n_jobs = 1
)

# Extract results
trials <- tibble(res[[1]])
evokeds <- tibble(res[[2]])
clusters <- tibble(res[[3]])
# tfr_evokeds <- tibble(res[[4]])
# tfr_clusters <- tibble(res[[5]])
```

```{r, modeling, eval=run$modeling}
# Read single trial data
read_csv(trials_file, col_types = cols(
  participant_id = col_factor(),
  item_id = col_factor(),
  phase = col_factor(),
  condition = col_factor()
)) %>%
  # Mark unrealistically short RTs
  mutate(rt = ifelse(rt < 200, NA, rt))

# Filter relevant conditions for the main analysis
trials %>%
  mutate(condition = factor(condition, levels = c("Informed", "Naive"))) %>%
  drop_na() -> trials_main

# Contrast coding for phase
cbind(
  c("Pre-insight" = -1, "Insight" = 1, "Post-insight" = 0),
  c("Pre-insight" = 0, "Insight" = -1, "Post-insight" = 1)
) %>%
  t() %>%
  ginv() -> contrasts(trials_main$phase)

# Contrast coding for condition
cbind(c("Informed" = 1, "Naive" = -1)) %>%
  t() %>%
  ginv() -> contrasts(trials_main$condition)

# Construct model formula
form <- ~ phase * condition +
  (phase * condition | participant_id) +
  (phase * condition | item_id)

# Fit linear mixed models
deps <- c("P1", "N170", "N400")
map(deps, function(dep, model_formula = form, model_data = trials_main) {

  # Modify the formula such that fixed effects are always retained
  model_formula %<>%
    tabulate.formula() %>%
    mutate(block = replace(block, is.na(grouping), "fixed"))

  # Start a CPU cluster so that multiple models can be fitted in parallel
  n_cores <- detectCores()
  cl <- makeCluster(n_cores)

  # Find the best fitting model (see Matuschek et al., 2017, *JML*)
  build <- buildmer(
    buildmerControl = buildmerControl(
      formula = model_formula,
      data = model_data,
      args = list("control" = lmerControl(
        optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)
      )),
      direction = c("backward", "backward"),
      cl = cl,
      elim = LRTalpha(.20),
      calc.anova = TRUE,
      ddf = "Satterthwaite",
      dep = dep
    )
  )
  stopCluster(cl)

@@

  # Create list of returns
  list(
    "model" = build@model,
    "summary" = build@summary,
    "anova" = build@anova,
    "means" = em$emmeans,
    "contrasts" = em$contrasts
  ) %>%
    return()
}) %>%
  # Add ERP component names
  set_names(deps) -> models

# Save models
saveRDS(models, models_file)
```

```{r, table_1, include=TRUE}
# Read fitted models
models <- readRDS(models_file)

# View model summaries
walk(models, function(model) {
  print(formula(model$model))
  cat("\n")
  print(model$anova)
  cat("\n")
  print(model$contrasts)
  cat("\n\n")
})
```
